Verifying Demonstrations

### 2019-02-15 paper/intro.tex

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes in the order of hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and 
they can only give an estimate for a particular snapshot in time (\eg at the 
peak of the event). In particular, the existing methods cannot reliably 
estimate the cumulative participation count --- at least not without counting 
some persons multiple times --- which in turn increases the error of the 
estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable claims.
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
%\seb{in the sentence above I am not sure that the word unlinkable will be 
%  necessary clear}

\paragraph*{Contributions}

Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
way to securely estimate crowd counts in protests\footnote{%
  If location is ignored, it can be reduced to privacy-preserving yet 
  verifiable petitions.
}.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against the original protocol of 
Brands and Chaum) and \ac{DBTF}.
More importantly, it is public-key, handles malicious impersonating verifiers.
Since it is based on the Schnorr protocol, it provides a distance-bounded 
\ac{PK} for discrete logarithms.
That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
distance-bounding version and thus make general privacy-preserving, 
attribute-based credential systems distance bounding.

\paragraph*{Outline}

The paper is organized as follows.
\Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting.
We then discuss related work in terms of these properties in 
\cref{related-work}:
we first discuss the crowd counting methods that are classically used followed 
by work on location proof systems.

\Cref{definitions}, we formalize the notion of protest and the desired 
verifiability and privacy properties, and in \cref{building-blocks}, we give 
the relevant background on the building blocks of our solution.

\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security and formally verify it using 
Tamarin~\cite{TamarinDB}.

\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
estimation protocol.
We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
in \cref{PerformanceAnalysis}.

Finally, we discuss our assumptions and results in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

>>>>

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
Alice wants to estimate the number of participants to prove a certain support for her cause against Grace.
Bob, Carol and many others participate in the protest.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and 
they can only give an estimate for a particular snapshot in time. In particular, the existing methods cannot reliably 
estimate the cumulative participation count --- at least not without counting 
some persons multiple times --- which in turn increases the error of the 
estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. While one cannot
prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.

%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
%\seb{in the sentence above I am not sure that the word unlinkable will be 
%  necessary clear}

%\paragraph*{Contributions}

%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
%way to securely estimate crowd counts in protests\footnote{%
%  If location is ignored, it can be reduced to privacy-preserving yet 
%  verifiable petitions.
%}.
%
%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
%including \ac{DBDH} (which was an attack against the original protocol of 
%Brands and Chaum) and \ac{DBTF}.
%More importantly, it is public-key, handles malicious impersonating verifiers.
%Since it is based on the Schnorr protocol, it provides a distance-bounded 
%\ac{PK} for discrete logarithms.
%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
%distance-bounding version and thus make general privacy-preserving, 
%attribute-based credential systems distance bounding.

% The paper is organized as follows.
% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}). Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}). 
% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).

%The paper is organized as follows.
%\Cref{system-model}, we describe our system model and summarize the desired 
%properties for crowd counting.
%We then discuss related work in terms of these properties in 
%\cref{related-work}:
%we first discuss the crowd counting methods that are classically used followed 
%by work on location proof systems.
%
%\Cref{definitions}, we formalize the notion of protest and the desired 
%verifiability and privacy properties, and in \cref{building-blocks}, we give 
%the relevant background on the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
%\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
%estimation protocol.
%We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
%in \cref{PerformanceAnalysis}.
%
%Finally, we discuss our assumptions and results in \cref{Discussion} and give 
%our conclusions in \cref{Conclusion}.

### 2019-02-15 paper/location-proofs.tex
Breaks out crowd-counting-methods

\subsection{Location proofs}

>>>>

%\subsection{Location proofs}
\section{Distance bounding and location proofs}
\label{db-and-lp}
\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
%Time critical phases are complemented by slow phases during which the time is not taking into account. 
Slow phases, during which the time is not taken into account, complement the time critical phases.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in their vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as they can easily impersonate the prover as they have knowledge of their secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.

### 2019-02-15 paper/protest-model.tex

\subsection{Defining and formalizing protest and crowd estimation}%
\label{protest-model}

@@

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
to accept a participant as eligible.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being eligible if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

>>>>

\subsection{Protest,  crowd estimation}%
\label{protest-model}

@@

The strength function \(\str\) can be used to regulate the trust in the 
estimated participation count.
In general, \(\str\) can be defined as a weighted sum of the proof shares, 
\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
the witness corresponding to the proof share \(s_i\), and the threshold 
\(\theta\) represents the total trust needed to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called 
\emph{trusted witness}, participating in the protest. For instance, the role of 
the trusted witness could be taken by the independent journalist Jane.
In this situation, the weights would be 1 for trusted witnesses and 
0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a 
trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being eligible if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

### 2019-02-15 paper/protocol.tex

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutiae from related work are in~\cref{anon-cred-figures}.

Several entities are involved in our protocol.
First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key
%\footnote{%
%  This can be done by a centralized authority, such as a nation state with, 
%  \eg, passports; or a decentralized authority, as in the case of a a 
%  collective authority~\cite{collective-signing} powered by 
%  proof-of-personhood~\cite{proof-of-personhood}.
%}.
For simplicity, we assume that the \ac{CA} is a trusted third-party, but its role is only important to prevent Sybil attacks, so in practice we only need the \ac{CA} to not be aligned with the protesters. For instance, the role of the \ac{CA} can be assumed by a centralized authority, such as a nation state with, 
\eg, passports, and that would not impact the trust of a participation count for a protest \emph{against} this state. However, any pro-state demonstration in that context would be subject to Sybils. Another possibility would be to use a decentralized authority, as in the case of a 
collective authority~\cite{collective-signing} powered by 
proof-of-personhood~\cite{proof-of-personhood}.
The \ac{CA} is only involved in the setup phase.

Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}

During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration step, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration steps can be done once and the keys can be reused 
for an arbitrary number of protests.
Thus, the registration step could be easily integrated as part of the issuance 
of national identity cards, passports or \acp{eID}.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring}) and
verification (in \cref{ProtocolVerification}).

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by any \emph{logically} centralized 
  authority~\cite{SybilAttack}.
  Although a decentralized authority, as in the case of a collective 
  authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
  that this has scalability issues.
  See the detailed discussion in \cref{identity-limits}.
  We will also return to this topic in \cref{Discussion}.
}.
The \ac{CA} is only involved in the setup phase.

Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key~\((k, 
  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
  it} to the \ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration steps can be done once and the keys can be reused 
for an arbitrary number of protests.

### 2019-02-15 paper/system-model.tex
Adds another pointer to difference to petition

\section{System and adversary model}%
\label{system-model}

To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.

\subsection{System model and physical assumptions}%
\label{assumptions}

@@

We draw inspiration from the three traditionally desired properties for verifiability for voting:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

In addition to the verification requirements, we also need to define the 
privacy properties.
In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
\end{description}

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable (probably 
not possible) in our context since this will conflict with verifiability: in 
contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which conflicts with verifiability.

Thus, in our context the crucial property is therefore privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the participation 
proof (and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (\eg 
from a different protest).

\subsection{Adversary model}%
\label{adversary-model}

We consider two types of adversaries: 
\begin{enumerate*} 
\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
\end{enumerate*}

>>>>

\section{System model}%
\label{system-model}

To set the stage, we will now describe our system model including
assumptions and a summary of the desired properties for crowd
counting% and the adversary model
.

\subsection{Model and assumptions}%
\label{assumptions}

@@

We draw inspiration from properties for voting systems as formalized
in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
\end{description}

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting booths), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

Therefore in our context, the crucial property is  vote privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the participation 
proof (and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (from a different protest).

% \subsection{Adversary model}%
% \label{adversary-model}

% We consider two types of adversaries: 
% \begin{enumerate*} 
% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
% \end{enumerate*}
